---
title: "AMMSA -- Swedish Validation, Analyses with Demographics"
output: github_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
with_demo <- TRUE
source("ammsa_main-analysis.R")

library(ggplot2)
library(tidyr)
```

# Descriptive and Correlation Analysis

## Demographics

### Age

```{r}
ammsa %>% 
  summarise(
    mean = mean(age, na.rm = TRUE),
    sd = sd(age, na.rm = TRUE),
    median = median(age, na.rm = TRUE)
  )
```

```{r}
ammsa %>% 
  group_by(dem_01_gender) %>% 
  summarise(
    mean = mean(age, na.rm = TRUE),
    sd = sd(age, na.rm = TRUE),
    median = median(age, na.rm = TRUE)
  )
```

```{r}
ggplot(ammsa,
       aes(
         x = age
       )) +
  geom_histogram(
    binwidth = 5
  ) +
  scale_x_continuous(
    breaks = seq(18, 88, 5)
  ) +
  theme_classic()
```

```{r}
ggplot(ammsa,
       aes(
         x = age
       )) +
  facet_wrap(~ dem_01_gender) +
  geom_histogram(
    binwidth = 5
  ) +
  scale_x_continuous(
    breaks = seq(18, 88, 5)
  ) +
  theme_classic()
```

### Gender

1 = Woman

2 = Man

3 = Non-binary

4 = Other genders

```{r}
table(ammsa$dem_01_gender)
```

### Education

1 = Primary school

2 = High school or equivalent

3 = Post-high school education

13 = Studying bachelor's right now

4 = Vocational training

5 = Bachelor's

6 = Master's

7 = Doctorate

```{r}
table(ammsa$dem_02_edu)
```

### Occupation

1 = Studying

2 = Unemployed

3 = Working fulltime

4 = Working parttime

5 = Medical leave

6 = Retired

8 = Parental leave

```{r}
table(ammsa$dem_03_occu)
```

### Place of residence

1 = 

2 = 

3 = 

4 = 

5 = 

6 =

7 =

8 =

9 = 

```{r}
table(ammsa$dem_04_living)
```

### Political spectrum

```{r}
ammsa %>% 
  summarise(
    mean = mean(dem_05_rightleft_1, na.rm = TRUE),
    sd = sd(dem_05_rightleft_1, na.rm = TRUE),
    median = median(dem_05_rightleft_1, na.rm = TRUE)
  )
```

```{r}
ggplot(ammsa,
       aes(
         x = dem_05_rightleft_1
       )) +
  geom_histogram(
    binwidth = 1
  ) +
  scale_x_continuous(
    breaks = seq(0, 10, 1)
  ) +
  theme_classic()
```

### Correlations

```{r}
covergent_ci
```
