---
title: "AMMSA -- Swedish Validation, Main Analyses"
output: github_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
with_demo <- TRUE
source("ammsa_main-analysis.R")

library(ggplot2)
library(tidyr)
```

# Data screening and description

## Missing data

```{r}
sum(
  is.na(ammsa_scale)
)
```

## Bivariate correlations

### AMMSA Items

```{r}
ammsa_cor_ci
```

### With Other Measures

```{r}
covergent_ci
```

```{r}
scatter_grid
```

## Frequency distributions of AMMSA responses

```{r}
hist_grid
```

```{r}
ggplot(ammsa,
        aes(
          sample = ammsa_total
        )) +
geom_qq(
  distribution = qnorm
) +
geom_qq_line(
  distribution = qnorm
) +
theme_classic()
```

```{r, fig.asp = 1}
ammsa_scale %>% 
    pivot_longer(
        cols = everything(),
        names_to = "item",
        values_to = "value"
    ) %>% 
  ggplot(.,
         aes(
           x = value
         )) +
  facet_wrap(
    ~ item,
    nrow = 5) +
  geom_histogram(
    binwidth = 1
  ) +
  theme_classic()
```

## Multivariate normality

### Mardia's tests

```{r}
mardia(ammsa_scale)
```

### Mahalanobis distances

```{r}
cfa_cov <- cov(ammsa_scale)

cfa_means <- colMeans(ammsa_scale)

mahal <- mahalanobis(ammsa_scale, center = cfa_means, cov = cfa_cov)

mahal_p <- pchisq(mahal, df = ncol(ammsa_scale), lower.tail = FALSE)

ID <- 1:nrow(ammsa_scale)

mahal_data <- data.frame(ID, mahal, mahal_p)
```

```{r}
arrange(mahal_data, by = desc(mahal))
```

```{r}
ggplot(mahal_data,
        aes(
          sample = mahal
        )) +
geom_qq(
  distribution = qchisq,
  dparams = list(df = ncol(ammsa_scale))
) +
geom_qq_line(
  distribution = qchisq,
  dparams = list(df = ncol(ammsa_scale))
) +
theme_classic()
```

# Factor analysis

## One-factor model

```{r}
summary(ammsa_cfa_1_fit,
        standardized = TRUE,
        fit.measures = TRUE)
```

```{r}
standardizedsolution(ammsa_cfa_1_fit)
```

```{r}
semPlot::semPaths(ammsa_cfa_1_fit, 
                    what = "paths",
                    whatLabels = "std",
                    intercepts = FALSE,
                    residuals = FALSE,
                    curvePivot = TRUE,
                    layout = "circle",
                    sizeLat = 4,
                    sizeMan = 3,
                    groups = "latents",
                    nodeLabels = c(1:30, "RMA"))
```

## Seven-factor model

```{r}
summary(ammsa_cfa_7_fit,
        standardized = TRUE,
        fit.measures = TRUE)
```

```{r}
standardizedsolution(ammsa_cfa_7_fit)
```

```{r}
semPlot::semPaths(ammsa_cfa_7_fit, 
                  what = "paths",
                  whatLabels = "std",
                  intercepts = FALSE,
                  residuals = FALSE,
                  curvePivot = TRUE,
                  layout = "circle",
                  sizeLat = 4,
                  sizeMan = 3,
                  groups = "latents",
                  nodeLabels = node_names)
```

# Model comparison

```{r}
cfa_lrt
```

# Invariance testing

## One-factor model

```{r}
invar_cfa_1_fitind_1
invar_cfa_1_fitind_2
invar_cfa_1_fitind_3
invar_cfa_1_fitind_4
```

## Seven-factor model

```{r}
invar_cfa_7_fitind_1
invar_cfa_7_fitind_2
invar_cfa_7_fitind_3
invar_cfa_7_fitind_4
```

# Network modeling

```{r}
network_pars
```

```{r}
network_fit_ind
```

```{r}
qgraph(getmatrix(network_model_final, "omega"),
         labels = 1:30,
         layout = "spring",
         vsize = 4,
         edge.labels = TRUE,
         edge.label.cex = .40,
         edge.label.bg = "white",
         edge.label.position = .50,
         edge.color = "#151414",
         vTrans = 200,
         negDashed = FALSE)
```

## Centrality

```{r}
qgraph::centralityPlot(network_graph,
                       include = c("Strength", "Closeness", "Betweenness"))
```

```{r}
ammsa_strength
```

```{r}
ammsa_between
```

## Average Shortest Path Length (ASPL)

```{r}
centrality(network_graph)$ShortestPathLengths[centrality(network_graph)$ShortestPathLengths %>% upper.tri()] %>% 
  mean()
```

## Expected Influence

```{r}
centrality(network_graph)$OutExpectedInfluence %>% 
  sort()
```

## What would happen if you persuaded people?

### No persuasion, assuming moderate disagreement overall

```{r}
ammsa_sim_base_hist
```

### Strong persuasion to disagree with Item 23 ("On the Job Harassment")

```{r}
ammsa_sim_pers_hist
```

```{r}
t.test(ammsa_sim_pers$total, ammsa_sim_base$total)
```

