---
title: "AMMSA -- Swedish Validation, Exploratory Analyses"
output: github_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

with_demo <- FALSE

source("ammsa_main-analysis.R")
source("ammsa_exploratory-analysis.R")

library(ggplot2)
library(tidyr)
```

# IRMA Explorations

## Factor Analyses

### Unidimensional Model

```{r}
summary(irma_uni_fit,
        standardized = TRUE,
        fit.measures = TRUE)
```

```{r}
semPlot::semPaths(irma_uni_fit, 
                    what = "paths",
                    whatLabels = "std",
                    intercepts = FALSE,
                    residuals = FALSE,
                    curvePivot = TRUE,
                    layout = "circle",
                    sizeLat = 4,
                    sizeMan = 3,
                    groups = "latents",
                    nodeLabels = c(1:22, "RMA"))
```

### Four-Factor Model

```{r}
summary(irma_4_fit,
        standardized = TRUE,
        fit.measures = TRUE)
```

```{r}
semPlot::semPaths(irma_4_fit, 
                    what = "paths",
                    whatLabels = "std",
                    intercepts = FALSE,
                    residuals = FALSE,
                    curvePivot = TRUE,
                    layout = "tree2",
                    sizeLat = 4,
                    sizeMan = 3,
                    groups = "latents",
                    nodeLabels = c(1:22, "AFI", "DMT", "NR", "SL"))
```

### Bifactor Model

```{r}
summary(irma_bi_fit,
        standardized = TRUE,
        fit.measures = TRUE)
```

```{r}
semPlot::semPaths(irma_bi_fit, 
                    what = "paths",
                    whatLabels = "std",
                    intercepts = FALSE,
                    residuals = FALSE,
                    curvePivot = TRUE,
                    exoCov = FALSE,
                    layout = "tree2",
                    sizeLat = 4,
                    sizeMan = 3,
                    groups = "latents",
                    bifactor = "rma",
                    nodeLabels = c(1:22, "RMA", "AFI", "DMT", "NR", "SL"))
```

## Network Model

```{r}
network_pars_irma
```

```{r}
network_fit_ind_irm
```

```{r}
qgraph(getmatrix(network_model_final_irma, "omega"),
         labels = 1:22,
         layout = "spring",
         vsize = 4,
         edge.labels = TRUE,
         edge.label.cex = .40,
         edge.label.bg = "white",
         edge.label.position = .50,
         edge.color = "#151414",
         vTrans = 200,
         negDashed = FALSE)
```

## Centrality

```{r}
qgraph::centralityPlot(network_graph_irma,
                       include = c("Strength", "Closeness", "Betweenness"))
```

```{r}
irma_strength
```

```{r}
irma_between
```

## Average Shortest Path Length (ASPL)

```{r}
centrality(network_graph_irma)$ShortestPathLengths[centrality(network_graph_irma)$ShortestPathLengths %>% upper.tri()] %>% 
  mean()
```

## Expected Influence

```{r}
centrality(network_graph_irma)$OutExpectedInfluence %>% 
  sort()
```

## What would happen if you persuaded people?

### No persuasion, assuming moderate disagreement overall

```{r}
irma_sim_base_hist
```

### Strong persuasion to disagree with Item 20 ("Regretting Leading Men On")

```{r}
irma_sim_pers_hist
```

```{r}
t.test(irma_sim_pers$total, irma_sim_base$total)
```

# AMMSA Exploration

## Profiles of responses, by total score

```{r, fig.height = 6}
ammsa_profiles
```

